SST_patterns

### 2019-09-19 SST_patterns.Rmd
left_join

```{r}
load("Data/site_list_sub.Rdata")
load("Data/SACTN_US.RData")
load("Data/site_pixels.RData")
load("Data/OISST.RData")
OISST <- BC_avhrr_only_v2_Document_Document 
rm(BC_avhrr_only_v2_Document_Document )
load("Data/CMC.RData")
```

@@

#   return(pixels)
# }
# 
# # Pixel points
# site_pixels <- data.frame()
# for(i in 1:length(west$site)){
#   site <- site_transects[i,]
#   site_pixel <- transect.pixel(site, c(10000, 20000, 30000, 40000, 50000)) # RWS: fixed error
#   site_pixels <- rbind(site_pixels, site_pixel)
# }
# 
# # Bounding box
#   # Only one is made in order to know how large the the geom_point() squares should be made to match
# bbox <- data.frame(xmin = destPoint(p = site_pixels[1,2:3], b = 270, d = 12500)[1],
#                    xmax = destPoint(p = site_pixels[1,2:3], b = 90, d = 12500)[1],
#                    ymin = destPoint(p = site_pixels[1,2:3], b = 180, d = 12500)[2],
#                    ymax = destPoint(p = site_pixels[1,2:3], b = 0, d = 12500)[2])
# 
# # Determining the temperature at the various distances from the coast
# 
# # save(site_pixels, file = "Data/site_pixels.RData")
# load("Data/site_pixels.RData")
```

@@

@@

# Decided to work with OISST and CMC as both has a time series of 30years
#

@@

sat_pixels <- sat_data %>% 
  select(product, lon, lat) %>%
  unique()

## For testing the nest/map pipeline
# df <- sat_pixels %>% 
#   filter(product == "MUR", site == "Lamberts Bay") %>% 
#   select(-c(product, site))

match_func <- function(df){
  df <- na.omit(df) %>% 
    dplyr::rename(lon_sat = lon, lat_sat = lat)
  match_index <- knnx.index(data = as.matrix(site_pixels[,2:3]),
                    query = as.matrix(df[,1:2]), k = 1)
  res <- cbind(site_pixels[match_index,], df)
  return(res)
}

pixel_match <- sat_data %>% 
  group_by(product) %>% 
  nest() %>% 
  mutate(match = purrr:::map(data, match_func)) %>% 
  select(-data) %>%
  unnest(match) %>% 
  unite(col = combi, lon, lat, sep = "/", remove = F)

# You may then use the 'pixel_match' object to filter out the desired pixels from the full satellite products
# one time series for each product for each pixel at each distance for each site that you may then
dataset_filt <- function(df){
  filtered_products <- OISST %>% 
  unite(col = combi, lon, lat, sep = "/", remove = F) %>% 
  filter(combi %in% pixel_match$combi)
}

OISST_fil <- dataset_filt(df = OISST)
CMC_fil <- dataset_filt(df = CMC)

# Repeat this on MODIS K10 and another time series of 10 years

>>>>

```{r}
load("Data/site_list_sub.Rdata")
load("Data/SACTN_US.RData")
load("Data/site_pixels.RData") # 5 decimal places
load("Data/OISST.RData") # 2 decimal places
OISST <- BC_avhrr_only_v2_Document_Document 
rm(BC_avhrr_only_v2_Document_Document )
load("Data/CMC.RData") # 1decimal places
```

@@

#   return(pixels)
# }
# 
# # Pixel points
# site_pixels <- data.frame()
# for(i in 1:length(west$site)){
#   site <- site_transects[i,]
#   site_pixel <- transect.pixel(site, c(10000, 20000, 30000, 40000, 50000)) # RWS: fixed error
#   site_pixels <- rbind(site_pixels, site_pixel)
# }
# 
# # Bounding box
#   # Only one is made in order to know how large the the geom_point() squares should be made to match
# bbox <- data.frame(xmin = destPoint(p = site_pixels[1,2:3], b = 270, d = 12500)[1],
#                    xmax = destPoint(p = site_pixels[1,2:3], b = 90, d = 12500)[1],
#                    ymin = destPoint(p = site_pixels[1,2:3], b = 180, d = 12500)[2],
#                    ymax = destPoint(p = site_pixels[1,2:3], b = 0, d = 12500)[2])
# 
# # Determining the temperature at the various distances from the coast
# 
# # save(site_pixels, file = "Data/site_pixels.RData")
# load("Data/site_pixels.RData")

@@

site_pixels$lat<-round(site_pixels$lat, 1) #CMC is to 1 decimal place and OISST is to 2
site_pixels$lon<-round(site_pixels$lon, 1)

@@

# Decided to work with OISST and CMC as both has a time series of 30years

@@

sat_pixels <- sat_data %>% 
  select(product, lon, lat) %>%
  unique()
## For testing the nest/map pipeline
# df <- sat_pixels %>% 
#   filter(product == "MUR", site == "Lamberts Bay") %>% 
#   select(-c(product, site))

match_func <- function(df){
  df <- na.omit(df) %>% 
    dplyr::rename(lon_sat = lon, lat_sat = lat)
  match_index <- knnx.index(data = as.matrix(round(site_pixels[,2:3]),1),
                    query = as.matrix(df[,1:2]), k = 1)
  res <- cbind(site_pixels[match_index,], df)
  return(res)
}

pixel_match <- sat_data %>% 
  group_by(product) %>% 
  nest() %>% 
  mutate(match = purrr:::map(data, match_func)) %>% 
  select(-data) %>%
  unnest(match) #%>% 
  #unite(col = combi, lon, lat, sep = "/", remove = F)

pixel_match$lat<-round(pixel_match$lat, 1) #CMC is to 1 decimal place and OISST is to 2
pixel_match$lon<-round(pixel_match$lon, 1)

# You may then use the 'pixel_match' object to filter out the desired pixels from the full satellite products
# one time series for each product for each pixel at each distance for each site that you may then
# dataset_filt <- function(df){
#   filtered_products <- df %>% 
#   unite(col = combi, lon, lat, sep = "/", remove = F) #%>% 
#   #filter(combi %in% pixel_match$combi)
# }

# OISST_fil <- dataset_filt(df = OISST)
# CMC_fil <- dataset_filt(df = CMC)
# 
# 
# pixel_match$lat
# pixel_match$lon

filterted_product <- function(df){
  extracted <- pixel_match %>% 
  right_join(df, by = c("lon", "lat")) %>% 
  select(date,temp,lat,lon)
}

OISST_fil <- filterted_product(df = OISST)
CMC_fil <- filterted_product(df = CMC)

# Next to run upwelling index
```
